\bf Adaptive Mesh Refinement for 1-D Hyperbolic PDEs

### 2015-03-04 paper_draft1.tex
modified paper outline

%\begin{center}
\title{\bf Adaptive Mesh Refinement for Hyperbolic PDE}
\author{}
\maketitle
%\end{center}

@@

\section{Outline}
\begin{itemize}
\item

\end{itemize}

>>>>

%\begin{center}
\title{\bf Adaptive Mesh Refinement for 1-D Hyperbolic PDEs}
\author{ 
Saumya Sinha\footnote{Department of Applied Mathematics, University of Washington, Seattle, Washington
U.S.A.
Email:\texttt{saumya@uw.edu}},
Kenneth J. Roche\footnote{
High Performance Computing Group, 
Pacific Northwest National Laboratory,
1 Battelle Road,
Richland, Washington 
U.S.A. 
Email:\texttt{kenneth.roche@pnnl.gov}} 
}
\maketitle
%\end{center}

@@

\newpage
\tableofcontents
\listoffigures
\listoftables
\newpage

\section{Overview of Paper}
\subsection{Description of AMR (Fig 2.1 from Berger-Leveque)}
\subsection{Wave-propagation for 1D equations -updating grid interfaces (section 4 of paper)}
\subsection{Pseudo-code for AMR}
\subsection{Comment on determining refinement - error estimation}
\subsection{Notes on flagging cells, boundary conditions}

\section{Examples of 1D AMR}
\subsection{scalar advection}
\subsection{linear system (acoustics)}
\subsection{variable coefficient (color equation)}
\subsection{nonlinear scalar (Burgers)}
\subsection{nonlinear system (shallow water or acoustics with pressure term)}

\section{Results}
\subsection{Numerical experiments for the 1D cases}
\subsection{Software implementation}

\section{Summary}

%\section{Outline}
%\begin{itemize}
%\item Overview of paper
%\begin{itemize}
%\item Description of AMR, Figure 2.1 from Berger-Leveque paper.
%\item Wave propagation form for 1-d equations. Updating on grid interfaces, section 4 of paper
%\item pseudo-code for algorithm, similar to that on page 2310 of paper.
%\item comment on error estimation -determining refinement
%\item notes on: flagging cells, boundary conditions
%\end{itemize}
%\item Examples of 1D AMR
%\begin{itemize}
%\item scalar advection
%\item linear system (e.g. Acoustics)
%\item variable coefficient (e.g. Color equation)
%\item nonlinear scalar (burgers)
%\item nonlinear system (shallow water or acoustics with pressure term)
%\end{itemize}
%\item Results of Numerical Experiments for the 1D cases
%\item Software 
%
%\end{itemize}
